Figures to insert in text

### 2018-03-16 Chapters/Introduction.tex
quotes
one life

@@

\caption{Slides from an old Linhares class; a viewpoint that has influenced the choice of topics found in this thesis.   In the history of computing business, the most interesting level of analysis seems to be that of the \emph{platform}.  It is where things can get built on top of, and communities emerge, and standards fight against each other, and fortunes are built or lost.  It is, in a sense, a major part of the Big Drama of our moment in history. Each time a new computing platform appears, it seems as the opportunities are ripe for the taking; as if a multitude of doors have opened simultaneously.  Note that the slides were made in 2007, and expected an AI-based `semantic revolution` by 2015 \citep{only-one-life}.  In between, both the iPhone (and competitors) and Bitcoin (and competitors) have created giant platforms on top of which immense wealth has been created (Uber, Instagram, etc, on the case of smartphones; and exchanges, miners, investors, payment processors, etc., in the case of blockchains).  Linhares's thesis is that students should (i) expect new, unexpected, technological platforms, (ii) rapidly identify them, and (iii) throw their energy at them, as they offer leverage to make an asymmetric impact.
\label{fig:onelife}}
\end{figure}

>>>>

\begin{flushright}{\slshape
	It is still an unending source of surprise for me to see \\
	how a few scribbles on a blackboard or on a sheet of paper\\
	could change the course of human affairs.} \\ \medskip
    --- Stanislaw Ulam
\end{flushright}

@@

\caption{Slides from an old Linhares class; a viewpoint that has influenced the choice of topics found in this thesis.   In the history of computing business, the most interesting level of analysis seems to be that of the \emph{platform}.  It is where things can get built on top of, and communities emerge, and standards fight against each other, and fortunes are built or lost.  It is, in a sense, a major part of the Big Drama of our moment in history. Each time a new computing platform appears, it seems as the opportunities are ripe for the taking; as if a multitude of doors have opened simultaneously.  Note that the slides were made in 2007, and expected an AI-based `semantic revolution` by 2015 \citep{only-one-life}.  In between, both the iPhone (and competitors) and Bitcoin (and competitors) have created giant platforms on top of which immense wealth has been created (Uber, Instagram, etc, on the case of smartphones; and exchanges, miners, investors, payment processors, etc., in the case of blockchains).  The key point is that we should (i) expect new, unforeseen, technological platforms, (ii) rapidly identify them, and (iii) throw their energy at them, as they offer leverage to make an asymmetric impact.
\label{fig:onelife}}
\end{figure}
